---
title: "Migrate Output Analysis"
author: "Eric Crandall"
date: "9/30/2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

source("/Users/eric/github/ibdsims/migrate_harvester_functions.R")
```

# Migrate Output Analysis
#### 9/30/16
Here I will borrow and modify code that I used in the ToBo analysis to quickly look at marginal likelihoods across the seven different models that I tested using both msat and mtdna datasets. I modified it and gave the three functions `migrate_harvester`, `bfcalcs`, and `getmodels` into their own file to be sourced.

### Harvesting the likelihoods
for mtDNA
```{r}
wd<-"/Users/eric/Datasets/simulations/ibdsim/migrate_pareto2_mtdna_results"
models<-c("panmixia","5island","5stepping.stone","5stepping.stone1","10island","10stepping.stone","10stepping.stone1")
setwd(wd)
marglikes<-migrate_harvester(wd=wd,models=models)
bftable<-lapply(marglikes,bfcalcs,ml="bezier.corrected")
bftable

```
Dang, it is choosing 5island!
