---
title: "Migrate Output Analysis"
author: "Eric Crandall"
date: "9/30/2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(width = 100)
source("/Users/eric/github/ibdsims/migrate_harvester_functions.R")
```

# Migrate Output Analysis
#### 9/30/16
Here I will borrow and modify code that I used in the ToBo analysis to quickly look at marginal likelihoods across the seven different models that I tested using both msat and mtdna datasets. I modified it and gave the three functions `migrate_harvester`, `bfcalcs`, and `getmodels` into their own file to be sourced.

## Harvesting the likelihoods
### mtDNA - Pareto 2 IBD model
```{r mtDNA-Pareto, echo=F}
wd<-"/Users/eric/Datasets/simulations/ibdsim/migrate_pareto2_mtdna_results"
models<-c("panmixia","5island","5stepping.stone","5stepping.stone1","10island","10stepping.stone","10stepping.stone1")
setwd(wd)
marglikes<-migrate_harvester(wd=wd,models=models)
bftable<-lapply(marglikes,bfcalcs,ml="bezier.corrected")
bftable
bfsum_mtdna_pareto2<-bfcalcs_reps(bftable, models=models)
print("Final Result - 3 reps")
bfsum_mtdna_pareto2

```
Dang, it is choosing 5island!

### mtDNA - singlepop panmixia model
```{r mtDNA-singlepop, echo=F}
wd<-"/Users/eric/Datasets/simulations/ibdsim/migrate_singlepop_mtdna_results"
models<-c("panmixia","5island","5stepping.stone","5stepping.stone1","10island","10stepping.stone","10stepping.stone1")
setwd(wd)
marglikes<-migrate_harvester(wd=wd,models=models)
bftable<-lapply(marglikes,bfcalcs,ml="bezier.corrected")
bftable
bfsum_mtdna_singlepop<-bfcalcs_reps(bftable, models=models)
print("Final Result - 3 reps")
bfsum_mtdna_singlepop


```
Great! This chose panmixia


### Replicate 1 of msat Pareto2 IBD model
```{r msats-Pareto2_rep1, echo=F}
wd<-"/Users/eric/Datasets/simulations/ibdsim/migrate_pareto2_msats_results_rep1"
models<-c("panmixia","5island","5stepping.stone","5stepping.stone1","10island","10stepping.stone","10stepping.stone1")
setwd(wd)
marglikes<-migrate_harvester(wd=wd,models=models,multilocus = T)
bftable<-lapply(marglikes,bfcalcs,ml="bezier.corrected")
bftable
bfsum_pareto2<-bfcalcs_reps(bftable, models=models)
print("Final Result - 3 reps")
bfsum_pareto2

```
This chose 10 deme stepping stone-2 parameter model

### Replicate 2 of msat Pareto2 IBD model
```{r msats-Pareto2_rep2, echo=F}
wd<-"/Users/eric/Datasets/simulations/ibdsim/migrate_pareto2_msats_results_rep2"
models<-c("panmixia","5island","5stepping.stone","5stepping.stone1","10island","10stepping.stone","10stepping.stone1")
setwd(wd)
marglikes<-migrate_harvester(wd=wd,models=models,multilocus = T)
bftable<-lapply(marglikes,bfcalcs,ml="bezier.corrected")
bftable
bfsum_pareto2<-bfcalcs_reps(bftable, models=models, reps=2)
print("Final Result - 2 reps")
bfsum_pareto2

```
This gave ambiguous results (p>0.05)

### Replicate 3 of msat Pareto2 IBD model
```{r msats-Pareto3, echo=F}
wd<-"/Users/eric/Datasets/simulations/ibdsim/migrate_pareto2_msats_results_rep3"
models<-c("panmixia","5island","5stepping.stone","5stepping.stone1","10island","10stepping.stone","10stepping.stone1")
setwd(wd)
marglikes<-migrate_harvester(wd=wd,models=models,multilocus = T)
bftable<-lapply(marglikes,bfcalcs,ml="bezier.corrected")
bftable
bfsum_pareto2<-bfcalcs_reps(bftable, models=models, reps=2)
print("Final Result - 2 reps")
bfsum_pareto2

```
This gave ambiguous results (p>0.05)

### Replicate 4 of msat Pareto2 IBD model
```{r msats-Pareto4, echo=F}
wd<-"/Users/eric/Datasets/simulations/ibdsim/migrate_pareto2_msats_results_rep4"
models<-c("panmixia","5island","5stepping.stone","5stepping.stone1","10island","10stepping.stone","10stepping.stone1")
setwd(wd)
marglikes<-migrate_harvester(wd=wd,models=models,multilocus = T)
bftable<-lapply(marglikes,bfcalcs,ml="bezier.corrected")
bftable
```
This chose the 10 deme stepping-stone 2 parameter model

### Replicate 5 of msat Pareto2 IBD model
```{r msats-Pareto5, echo=F}
wd<-"/Users/eric/Datasets/simulations/ibdsim/migrate_pareto2_msats_results_rep5"
models<-c("panmixia","5island","5stepping.stone","5stepping.stone1","10island","10stepping.stone","10stepping.stone1")
setwd(wd)
marglikes<-migrate_harvester(wd=wd,models=models,multilocus = T)
bftable<-lapply(marglikes,bfcalcs,ml="bezier.corrected")
bftable
```

### Replicate 1 of msat singlepop panmixia model
```{r msats-Panmixia1, echo=F}
wd<-"/Users/eric/Datasets/simulations/ibdsim/migrate_singlepop_msats_results"
models<-c("panmixia","5island","5stepping.stone","5stepping.stone1","10island","10stepping.stone","10stepping.stone1")
setwd(wd)
marglikes<-migrate_harvester(wd=wd,models=models,multilocus = T)
bftable<-lapply(marglikes,bfcalcs,ml="bezier.corrected")
bftable
```
