---
title: "mtdna_marginal_likelihood"
author: "Eric Crandall"
date: "November 4, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(width = 100)
source("/Users/eric/github/ibdsims/migrate_harvester_functions.R")
models<-c("10stepping.stone","5stepping.stone","10stepping.stone1","5stepping.stone1","10island","5island","panmixia")
```

## Migrate results for datasets simulated with a growth phase 10,000 generations in the past

### Replicates 1 of mtDNA panmixia with Ne=1,000,000
```{r mtdna_panmixia, echo=F}

```


### Replicates of mtDNA stepping stone model with m=0.1 and Ne = 10,000 Nm=1,000
```{r nl4_m0.1, echo=F}
wd<-"/Users/eric/Datasets/simulations/ibdsim/migrate_mtdna_g10k_nl4_m0.1"
bflist_g10k_nl4_m0.1<-list()
for(r in 1:10){
  wd2<-file.path(wd,paste("simrep",r,sep=""))
  marglikes<-migrate_harvester(wd=wd2,models=models,multilocus = F,quiet = T)
  bftable<-lapply(marglikes,bfcalcs,ml="bezier.corrected")
  bflist_g10k_nl4_m0.1[r]<-bftable
  print(r)
  print(bftable)
}
```

### Replicates of mtDNA stepping stone model with m=0.01 and Ne = 10,000 (Nm=100)
```{r nl4_m0.01, echo=F}
wd<-"/Users/eric/Datasets/simulations/ibdsim/migrate_mtdna_g10k_nl4_m0.01"
bflist_g10k_nl4_m0.01<-list()
for(r in 1:10){
  wd2<-file.path(wd,paste("simrep",r,sep=""))
  marglikes<-migrate_harvester(wd=wd2,models=models,multilocus = F,quiet = T)
  bftable<-lapply(marglikes,bfcalcs,ml="bezier.corrected")
  bflist_g10k_nl4_m0.01[r]<-bftable
  print(r)
  print(bftable)
}
```



### Replicates of mtDNA stepping stone model with m=0.01 and Ne = 100,000 (Nm=1,000)
```{r nl5_m0.01, echo=F}
wd<-"/Users/eric/Datasets/simulations/ibdsim/migrate_mtdna_g10k_nl5_m0.01"
bflist_g10k_nl5_m0.01<-list()
for(r in 1:10){
  wd2<-file.path(wd,paste("simrep",r,sep=""))
  marglikes<-migrate_harvester(wd=wd2,models=models,multilocus = F,quiet = T)
  bftable<-lapply(marglikes,bfcalcs,ml="bezier.corrected")
  bflist_g10k_nl5_m0.01[r]<-bftable
  print(r)
  print(bftable)
}
```

### Replicates of mtDNA stepping stone model with m=0.001 and Ne = 100,000 (Nm=100)
```{r nl5_m0.001, echo=F}
wd<-"/Users/eric/Datasets/simulations/ibdsim/migrate_mtdna_g10k_nl5_m0.001"
bflist_g10k_nl5_m0.001<-list()
for(r in 1:10){
  wd2<-file.path(wd,paste("simrep",r,sep=""))
  marglikes<-migrate_harvester(wd=wd2,models=models,multilocus = F,quiet = T)
  bftable<-lapply(marglikes,bfcalcs,ml="bezier.corrected")
  bflist_g10k_nl5_m0.001[r]<-bftable
  print(r)
  print(bftable)
}
```

### Replicates of mtDNA stepping stone model with m=0.001 and Ne = 1,000,000 (Nm=1,000)
```{r nl6_m0.001, echo=F}
wd<-"/Users/eric/Datasets/simulations/ibdsim/migrate_mtdna_g10k_nl6_m0.001"
bflist_g10k_nl6_m0.001<-list()
for(r in 1:10){
  wd2<-file.path(wd,paste("simrep",r,sep=""))
  marglikes<-migrate_harvester(wd=wd2,models=models,multilocus = F,quiet = T)
  bftable<-lapply(marglikes,bfcalcs,ml="bezier.corrected")
  bflist_g10k_nl6_m0.001[r]<-bftable
  print(r)
  print(bftable)
}
```

### Replicates of mtDNA stepping stone model with m=0.0001 and Ne = 1,000,000 (Nm=100)
```{r nl6_m0.0001, echo=F}
wd<-"/Users/eric/Datasets/simulations/ibdsim/migrate_mtdna_g10k_nl6_m0.0001"
bflist_g10k_nl6_m0.0001<-list()
for(r in 1:10){
  wd2<-file.path(wd,paste("simrep",r,sep=""))
  marglikes<-migrate_harvester(wd=wd2,models=models,multilocus = F,quiet = T)
  bftable<-lapply(marglikes,bfcalcs,ml="bezier.corrected")
  bflist_g10k_nl6_m0.0001[r]<-bftable
  print(r)
  print(bftable)
}
```

### Taking the means of the model probabilities across replicates

```{r modelprobs}
library(reshape2)
finalprobs<-data.frame(models)
for(sim in ls(pattern="bflist")){
  # this takes each of those lists and gets the model probabilities out for each model
  probs<-matrix(as.numeric(laply(get(sim), as.matrix)[,,7]),nrow=10)
  # take the mean model probability for each model
  probs2<-data.frame(apply(probs,2,mean))
  finalprobs<-cbind(finalprobs,probs2)
}
names(finalprobs)<-c("models",ls(pattern="bflist"))

longprobs<-melt(finalprobs,id.vars = "models",variable.name = "Simulation",value.name="Model Probability")
longprobs$models<-factor(longprobs$models, levels=models)
longprobs$Simulation<-factor(longprobs$Simulation, levels=c("bflist_g10k_nl4_m0.01","bflist_g10k_nl5_m0.001","bflist_g10k_nl6_m0.0001","bflist_g10k_nl4_m0.1","bflist_g10k_nl5_m0.01","bflist_g10k_nl6_m0.001"),labels=c("Ne = 10,000\nm = 0.01","Ne = 100,000\nm = 0.001","Ne = 1,000,000\nm = 0.0001","Ne = 10,000\nm = 0.1","Ne = 100,000\nm=0.01","Ne = 1,000,000\nm = 0.001"))
ggplot(data=longprobs,aes(x=Simulation,y=`Model Probability`)) + geom_bar(stat="identity",aes(fill=models)) + scale_fill_brewer(palette = "RdYlBu")

```
