---
title: "mtDNA analyses"
author: "Eric Crandall"
date: "September 9, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("hierfstat")
library("adegenet")
library("pegas")
library("ape")
library("strataG")
```

## Loading simulated mtDNA data and making a haplotype network

```{r, echo=F}
#https://arundurvasula.wordpress.com/2016/02/24/haplotype-networks-in-r/

c <- ape::read.nexus.data("./stepstone_mtdnas_m.01/mtdna_stepstone_m.01_AllIndividuals_rep1.nex")
d <- as.DNAbin(c)
e <- dist.dna(d)
h <- pegas::haplotype(d)
h <- sort(h, what = "label")
pop<-c(1,rep(5,20), rep(15,20), rep(25,20), rep(35,20), rep(45,20), rep(55,20), rep(65,20), rep(75,20), rep(85,20), rep(95,20))
net <- pegas::haploNet(h)
i<-stack(setNames(attr(h, "index"), rownames(h)))
ind.hap<- table(hap=i$ind, pop=pop)
plot(net, size=attr(net, "freq"), scale.ratio=0.2, pie=ind.hap,legend=F, labels=F)
legend("topleft", colnames(ind.hap), col=rainbow(ncol(ind.hap)), pch=19, ncol=2)
```

#maybe convert to gtypes with pop as populations, then compute IBD etc.

```{r convert}
g<-DNAbin2genind(d[2:201],pop=pop[-1])
gt<-sequence2gtypes(d[2:201],strata=pop[-1])
```

```{r analyze}
pwtest<-pairwiseTest(gt)
statPhist(gt,nrep = 100)
fusFs(gt[,,1])

#read in locations on the lattice
latdists<-read.table("distances.txt")
latdists<-dist(latdists)

phist_mtdna<-as.dist(pwtest$pair.mat$PHIst)
ibd<-mantel.randtest(phist_mtdna,latdists)
plot(latdists, phist_mtdna)
abline(lm(phist_mtdna~latdists))
```

```{r ibdloop, echo=F}
latdists<-read.table("distances.txt")
latdists<-dist(latdists)
par(mfrow=c(5,2))
plots<-list()

for(m in list.files(path="./stepstone_mtdnas_m.01", pattern="AllIndividuals_rep[0-9].nex")){
  
  #read in data and convert to gtypes
  nexus <- ape::read.nexus.data(paste("./stepstone_mtdnas_m.01/",m,sep=""))
  dna <- as.DNAbin(nexus)
  gt<-sequence2gtypes(dna[2:201],strata=pop[-1])
  print(m)
  
  pwtest<-pairwiseTest(gt,nrep = 0, stats="phist",quietly=T) # calculate pairwise Phist
  phist_mtdna<-as.dist(pwtest$pair.mat$PHIst) #grab the Phist table
  ibd<-mantel.randtest(phist_mtdna,latdists) # calculate Mantel test
  plots[[m]]<-ggplotRegression(lm(as.vector(phist_mtdna)~as.vector(latdists)))
  
  #  plot(latdists, phist_mtdna, xlab="", ylab="", las=1,main=paste("r =",round(ibd$obs,2),"p =",round(ibd$pvalue,2)))
#  abline(lm(phist_mtdna~latdists))
}




  
  


